Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex

\subsection{A new family of mechanisms}
\label{sec_exp}
In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
probability distributions.
The idea is that $\expmech$ will sample and output a distribution with higher probability when
it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
distributions as opposed to a metric over the parameters that represent it. In this work we will
use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
Given a prior distribution $\dirichlet{\valpha}$,
we define the follwing set  where the mechanism will sample from:
\[
  \candidateset{\valpha}=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
\]
In general $|\candidateset{\valpha}|=\binom{n + 1}{|\mathcal{X}| - 1}$ when $\valpha\in\mathcal{X}^n$. In the specific case of $|\mathcal{X}|=2$ with $\valpha=(\alpha,\beta)$,
that is the Beta-Binomial model, the above reduces to:
\[
  \{(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha,  \Delta\alpha=\sum x_i, \dataobs\in \{0,1\}^n\}
\]

@@

\paragraph{Experiments on Real Data Sets in Beta-binomial Model}
We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}. Each data set contains 1 binary variable, which applys to our Beta-binomial model. By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend. The second and third data set are the THERAPY data, where $1$ means patient with disease is cured and $1$ means not. The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge. The size of the four data set are $731, 90, 294, 90$. The accuracy are shown in Figure \ref{fig_real_2d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_2d}
\end{figure}

\paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
We use three real data sets from the same repository repository. Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which applys to our 3 dimension Dirichlet-multinomial model. By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions. The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the 2 diseases. The size of the four data set are $731, 90, 90$. The accuracy are shown in Figure \ref{fig_real_3d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata_3d.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_3d}
\end{figure}

\subsection{Privacy Evaluation}
\label{subsec_experiment_privacy}
In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section. The $(\epsilon, \delta)$ - differential privacy we proved in Sec. \ref{sec_ehds} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism. We calculate the concrete privacy value in following ways wrt. the data size, and obtain plots in Fig. \ref{fig_privacy}.

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}

$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected.

>>>>

\subsection{A new family of mechanisms}
\label{sec_exp}
In this section, we explore  mechanism which we denote by $\expmech$. $\expmech$ is an instance
of the exponential mechanism \cite{talwar} where the scoring function is based on a metric over
probability distributions.
The idea is that $\expmech$ will sample and output a distribution with higher probability when
it is closer to the real posterior; importantly,  \emph{closer} is measured using a metric over probability
distributions as opposed to a metric over the parameters that represent it. In this work we will
use the Hellinger distance, but this approach could be extended to other $f$-divergences. 
Given a prior distribution $\dirichlet{\valpha}$,
we define the follwing set  where the mechanism will sample from:
\[
  \candidateset{\valpha}=\{\inferd{\valpha}{\vtheta}{\dataobs}\mid \dataobs \in \mathcal{X}^n\}.
\]
In general $|\candidateset{\valpha}|=\binom{n + 1}{|\mathcal{X}| - 1}$ when $\valpha\in\mathcal{X}^n$. In the specific case of $|\mathcal{X}|=2$ with $\valpha=(\alpha,\beta)$,
that is the Beta-Binomial model, the above reduces to:
\[
\candidateset{\valpha}=  \left \{(\alpha',\beta') ~\vline~ \begin{aligned} & \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha, \\ & \Delta\alpha={\textstyle \sum x_i}, \dataobs\in \{0,1\}^n \end{aligned} \right\}.
\]

@@

\paragraph{Experiments on Real Data Sets in Beta-binomial Model}
We use four real data sets from UCI Machine Learning repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}. Each data set contains 1 binary variable, which fits our Beta-binomial model. By setting the prior distribution as $\betad(1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend. The second and third data set are the THERAPY data, where $1$ means patient with disease is cured and $1$ means not. The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge. The size of the four data set are $731, 90, 294, 90$. The accuracy are shown in Figure \ref{fig_real_2d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_2d}
\end{figure}

\paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
We use three data sets from the same repository repository. Each data set contains one category variable of 3 values ($|\mathcal{X}| = 3$), which fits our 3 dimension Dirichlet-multinomial model. By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $\mathcal{X} = \{0,1,2\}$ stand for 3 weather conditions. The second and third data set are the THERAPY data, where $0,1,2 \in \mathcal{X}$ represent 3 types of the 2 diseases. The size of the four data set are $731, 90, 90$. The accuracy are shown in Figure \ref{fig_real_3d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata_3d.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_3d}
\end{figure}

The red box representing the $\expmech$ plays worst in terms of accuracy. While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using). The purple one representing the $\lexpmech$ although performs better than $\expmech$ and $\hexpmech$, but it is non-private.

\subsection{Privacy Evaluation}
\label{subsec_experiment_privacy}
In order to see our privacy behavior, we study the privacy loss under concrete cases. The $\epsilon$ - differential privacy we proved in Sec. \ref{sec_mechs} is just an upper bound, the $\epsilon$ in practice might be smaller than upper bound. We calculate the actual privacy loss of $\expmech$, $\lexpmech$ and $\hexpmech$ w.r.t. the data size, and obtain plots in Fig. \ref{fig_privacy}.

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
\caption{The privacy loss in practice under different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}

We can observe from Fig. \ref{fig_privacy} that the actual privacy loss of $\expmech$ and $\hexpmech$ are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected.
